Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-02 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

In Sec.~\ref{sec:Interval-Uncertainty}, we discussed how states
consistent with a QIVPM~$\bar{\mu}$ on the projectors in a subspace
of event~$\events'$. In particular, if $\events'$ commutes, $\bar{\mu}$
restricting on $\events'$ is essentially a classical IVPM, and Thm.~\ref{thm:Shapley}
claims that there is always a state~$\rho$ consistent with $\bar{\mu}$.
In this section, we want to shift our attention to consider states
consistent with $\bar{\mu}$ on every event, $\coreBorn\left(\bar{\mu},\events\right)$,
so that these states could characterize $\bar{\mu}$ comprehensively.
When the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$ becomes
quantum probability measure~\citep{HOSTunpublished}. In this situation,
Gleason's theorem claims that there is always a unique state consistent
with $\bar{\mu}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum},
and this state can easily construct $\bar{\mu}$ according to the
Born rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. However,
if we consider general QIVPMs mapping to an \emph{arbitrary} set of
intervals, there is a QIVPM that no state can be consistent with it.

>>>>

In Sec.~\ref{sec:Interval-Uncertainty}, we discussed how states
consistent with a QIVPM~$\bar{\mu}$ on the projectors in a subspace
of event~$\events'$. In particular, if $\events'$ commutes, $\bar{\mu}$
restricting on $\events'$ is essentially a classical IVPM, and Thm.~\ref{thm:Shapley}
claims that there is always a state~$\rho$ consistent with $\bar{\mu}$.
In this section, we want to shift our attention to consider states
consistent with $\bar{\mu}$ on every event, $\coreBorn\left(\bar{\mu},\events\right)$,
so that these states could characterize $\bar{\mu}$ comprehensively.
When the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$ becomes
quantum probability measure~\citep{HOSTunpublished}. In this situation,
Gleason's theorem claims that there is always a unique state consistent
with $\bar{\mu}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum},
and this state can easily induce $\bar{\mu}$ according to the Born
rule~\citep{Born1983,peres1995quantum,544199,Jaeger2007}. However,
if we consider general QIVPMs mapping to an \emph{arbitrary} set of
intervals, there is a QIVPM that no state can be consistent with it.
